### 2019-02-26 appendices/proofs.tex
Revert changes to types

  \case
    {$\userule{H-Empty}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\beta$ and $\Sigma\infers s$, the \refrule{H-Empty} rule additionally gives us that $v:\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers\Enter \tau:\Task\tau$.}

>>>>

  \case
    {$\userule{H-Empty}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\tau$ and $\Sigma\infers s$, the \refrule{H-Empty} rule additionally gives us that $v:\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers\Enter \tau:\Task\tau$.}
